### 2021-07-22 doc/thesis/chapters/hls.tex
directives

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Compiler Directives}

e.g. \#pragma's

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Optimization Directives}

The HLS code can be instumented with additional optimization directives.
This is used to provide the HLS compiler with additional information and instruct it on how to implement certain parts of the code in RTL.\\

Directives can be applied to interfaces, functions, loops, arrays or code regions.
The directives can be written in a Tcl file that is provided to the HLS project, or in the design code directly, in the form of a pre-processor pragma.
Both variants have their advantages and disadvantages.\\

Examples for such directives are optimization strategies for thoughput and dataflow optimization, such as pipelining or loop unrolling.
Also the implementation of the required interface types, such as various AXI interfaces, is controlled with directives.\\

Since this topic is very comprehensive, it cannot be covered into more detail here.
For further information, refer to the user guide \cite{VivadoUgHLS}.

@@
